### 2012-12-24 inst/examples/allee.Rmd
different parameters
a new puzzle

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "allee-cache/", warning=FALSE)
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

```{r libraries, include=FALSE}
```
```{r graphing-options, include=FALSE}
```

```{r RickerAllee}
```

We use the model of Allen

```{r sdp-pars}
```

@@

```{r x0-obs}
x_0_observed <- K
xT <- 0
set.seed(1)
```

```{r sim-with-harvest}
```

We simulate data under this model, starting from a size of `r x_0_observed`.

We consider the observations as ordered pairs of observations of current stock size $x_t$ and observed stock in the following year, $x_{t+1}$.  We add the pseudo-observation of $0,0$.  Alternatively we could condition strictly on solutions passing through the origin, though in practice the weaker assumption is often sufficient.

```{r MLE-RickerAllee}
```

```{r gp-priors}
```

```{r gp-fit}
```

We fit a Gaussian process with

```{r gp-data, dependson="gp-fit"}
```

```{r gp-plot, dependson="gp-data"}
```

```{r gp-posteriors}
```

## The transition matrix of the inferred process

```{r persistence-test}
```

```{r gp-F-sim, dependson=c("persistence-test", "gp-data")}
```

```{r par-F-sim, dependson="persistence-test"}
```

```{r F-sim-plot, dependson=c("gp-F-sim", "par-F-sim")}
```

```{r gp-opt, dependson="gp-data"}
```

```{r true-opt}
```

```{r est-opt}
```

```{r policy_plot}
```

```{r othernoise}
```

```{r stationary_policy_only}
```

```{r simulate}
```

```{r tidy}
```

```{r sim-fish}
```

```{r sim-harvest}
```

```{r costs}
```

>>>>

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "allee/", warning=FALSE)
library(knitcitations)
```

```{r libraries, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
require(tgp)
library(kernlab)
require(MCMCpack)
require(plyr)

```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Fixed priors on hyperparameters, fixed model type.

```{r gp-priors}
s2.p <- c(50,50)  # inverse gamma mean is 
tau2.p <- c(20,1)
d.p = c(10, 1/0.01, 10, 1/0.01)
nug.p = c(10, 1/0.01, 10, 1/0.01) # gamma mean
s2_prior <- function(x) dinvgamma(x, s2.p[1], s2.p[2])
tau2_prior <- function(x) dinvgamma(x, tau2.p[1], tau2.p[2])
d_prior <- function(x) dgamma(x, d.p[1], scale = d.p[2]) + dgamma(x, d.p[3], scale = d.p[4])
nug_prior <- function(x) dgamma(x, nug.p[1], scale = nug.p[2]) + dgamma(x, nug.p[3], scale = nug.p[4])
beta0_prior <- function(x, tau) dnorm(x, 0, tau)
beta = c(0)
priors <- list(s2 = s2_prior, tau2 = tau2_prior, beta0 = dnorm, nug = nug_prior, d = d_prior, ldetK = function(x) 0)
```

```{r sdp-pars-fixed}
profit = function(x,h) pmin(x, h)
delta <- 0.01
OptTime = 20  # stationarity with unstable models is tricky thing
reward = 0
xT <- 0
z_g = function() rlnorm(1, 0, sigma_g)
z_m = function() 1+(2*runif(1, 0,  1)-1) * sigma_m
```

```{r RickerAllee-exp}
f <- RickerAllee
p <- c(1.1, 10, 5) 
K <- 10
allee <- 5
```

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.02
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

```{r }
seed_i <- 1

  Xo <- K # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
#  posteriors_plot(gp, priors) # needs trace=TRUE!
  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, OPT$true_D, OPT$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
```

```{r}
matrices_gp <- gp_transition_matrix(gp$ZZ.km, gp$ZZ.vark, x_grid, h_grid) # 
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, OptTime, xT, profit, delta, reward=reward)
```

```{r}
matrices_same <- gp_transition_matrix(sapply(x_grid, f, 0, p), gp$ZZ.vark, x_grid, h_grid) 
opt_same <- find_dp_optim(matrices_same, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```

```{r}
matrices_true <- f_transition_matrix(f, p, x_grid, h_grid, sigma_g)
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```

```{r}
dd <- melt(data.frame(x=x_grid, gp= opt_gp$D[,1], same=opt_same$D[,1], true=opt_true$D[,1]), id="x")
ggplot(dd) + geom_point(aes(x, value, col=variable))
```
